Figures

### 2020-05-15 manuscript/figures.Rmd
replace model metrics fig with a table

```{r depth_model_metrics, fig.cap = "Model fit and predictive accuracy metrics for all combinations of true (inlake slope, deepest point distance) and proxy (nearshore slope, visual center distance) metrics. Tiles are colored by their $R^2$ values and labeled with their RMSE values.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
# see 02_depth_model.Rmd
knitr::include_graphics("../figures/depth_model_metrics-1.pdf")
```

```{r 02_depth_model_importance, fig.cap = "Importance plot for random forest variables showing increase in mean square error. Higher values indicate greater importance to model predictions. See Equation 1 for a definition of geometric max depth. HUC4 ID is a 'dummy' variable of geographic (hydrologic subbasin) location.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/02_depth_model_importance-1.pdf")
```

>>>>

```{r depth_model_metrics, fig.cap = "Model fit and predictive accuracy metrics for all combinations of true (inlake slope, deepest point distance) and proxy (nearshore slope, visual center distance) metrics.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
# see tables/02_model_metrics.Rmd
knitr::include_graphics("../tables/02_model_metrics.pdf")
```
